---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

In this assignment, I chose to focus on the book related to the author George Orwell. 
When I was young, I read 1984 and Animal Farm and was impressed by these two books, and I had interest in analyzing my data with this author. 
As the data is provided by Seattle Public Library, the dataset includes columns like ‘UsageClass’, which means whether it is physical or digital form of book, ‘materialType’, which denotes if it is categorized as book, ebook, sound disc, or video disc, and other columns. 
In this report, I’m focusing on the average number of checkouts in this dataset, which year had the most/least checkouts, which year had the most/least checkouts for ebooks, how the number of print book checkouts is changed over time, and how many new checkouts there were when the most checkouts occurred. 



### Summary Information

The dataset I chose to analyze is close to the author George Orwell, and the average number of checkouts for this dataset is  **`r avg_num_checkout`**. 
The checkout year with the most checkouts for George Orwell is **`r max_checkout`**.
The checkout year with the least checkouts for George Orwell is **`r min_checkout`**.
Also, the checkout year with the most checkouts for ebooks is **`r max_ebook`**.
The checkout year with the least checkouts for ebooks is **`r min_ebook`**.
When looking at how the number of print book checkouts has changed over time, I compared the total number of checkouts now and five years ago. For the total check out now, it was **`r total_checkout_now`**. On the other hand, the total check out in 2018 is **`r total_checkout_2018`**. So, the difference the number of checkouts between 2018 and 2023 is **`r Difference_between_2023_and_2018`**. 
Finally, when looking at the chances in how many new checkouts there were when the most checkouts occurred, it is **`r most_new_checkouts`**. 







### The Dataset

- Who collected/published the data?  
This dataset was published by the Seattle Public Library.

- What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?
This dataset has columns like ‘UsageClass’, which means whether it is physical or digital form of book, ‘MaterialType’, which denotes if it is categorized as book, ebook, sound disc, or video disc, and ‘CheckoutYear’, ‘CheckoutMonth’, ‘Checkouts’, ‘Creator’, etc. 
The parameters include when the checkout occurred for this record and the number of times the title was checked out.   


- How was the data collected or generated? 
The dataset was first provided by the Seattle Public Library, and from the SPL Open Data portal, I chose to use my own datasets by filtering ‘George Orwell’ author. 
The dataset made for my own use indicates that any column includes ‘George Orwell’ such as either in the ‘Creator’ column or in the ‘Title’ column.  


- Why was the data collected?  
The purpose of the data collected was to analyze how many checkouts there are and how the number of the checkouts has changed over time. 

- What, if any, ethical questions do you need to consider when working with this data?  
Since this is collected and provided by the Seattle Public Library, I’m not sure what ethical issue there might have arised as it is the public source. 
However, we can’t assume that the dataset is 100% accurate and true. In other words, there might still be the possibility of fake information and data. 

- What are possible limitations or problems with this data?   (at least 200 words)




### First Trends Over Time Chart





``````{r, echo = FALSE, warning = FALSE, code = readLines("chart1_example.R")}
```

### Second Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The second chart that you will create and include will show another trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, code = readLines("chart2_example.R")}
```

### Your Choice

The last chart is up to you. It could be a line plot, scatter plot, histogram, bar plot, stacked bar plot, and more. Here are some requirements to help guide your design:

- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear legend title

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, code = readLines("chart2_example.R")}
```


